\chapter{Risk analysis}

\section{Risk identification}
We identified these main risks in our project planning:
\begin{itemize}
\item R1 -- Unrealistic schedule;
\item R2 -- Unavailability of staff caused by sudden problems (illness, other employments);
\item R3 -- The discovery of a badly designed project;
\item R4 -- Inability to find skilled developers for the code writing;
\item R5 -- Wrong functionality;
\item R6 -- Inability to create some critical algorithms;
\item R7 -- New members in staff.
\end{itemize}

Ranks go as follow: Negligible, Marginal, Serious, Catastrophic.

\begin{center}
\begin{tabular}{ccc}
\toprule
Risk	&	Probability	&	Effects	\\
\midrule
R1	&	High		&	Marginal	\\
R2	&	Moderate	&	Serious	\\
R3	&	Moderate	&	Serious	\\
R4	&	Hight		&	Catastrophic	\\
R5	&	Low		&	Catastrophic	\\
R6	&	Low		&	Serious	\\
R7	&	Low		&	Marginal	\\
\bottomrule
\end{tabular}
\end{center}

\section{Contingency strategies plan}
\subsection{R1 -- Unrealistic schedule}
Alert costumers to the possibility of delays and reorganize the project plan with new deadlines. Investigate buying-in components. Investigate use of a program generator. 

\subsection{R2 -- Unavailability of staff caused by sudden problems (illness, other employments)}
Reorganize resources allocation in order to give more work to someone that in future will have less work.

\subsection{R3 -- The discovery of a badly designed project}
Alert customers of delays, push back release date, and change the design as little as possible to fix it while salvaging as much as possible from what has already been done. Investigate buying-in components to replace badly designed ones.

\subsection{R4 -- Inability to find skilled developers for the code writing}
Investigate buying-in components. Analyse the possibility to train actual staff.

\subsection{R5 -- Wrong functionality}
Find out if it’s a requirement analysis problem or a implementation problem. In the first case derive traceability information in order to redesign that function. In the second case just recode the function. Maximize information hiding in the design.

\subsection{R6 -- Inability to create some critical algorithms}
Investigate buying-in components.

\subsection{R7 -- New members in staff}
Reorganize team and schedule. Reallocate staff to different tasks.

